Master's Project Journal

### 2019-04-17 thesis/NetworkImplemenation.tex
58.3

%TODO eugene
The delay line itself is shown in Figure \ref{fig:tdl_impl}, with each tap implemented by a pair of flip-flops and three inverters. For an $N$ bit width phase error detection, $2^{N-1}-1$ taps are required. In the case of this \ac{ADPLL}, a 5 bit two's complement error signal is required, thus the range of the signal is $[-16,15]\cap\mathbb{Z}$. If the range is made symmetrical, 15 taps are required to fill a signal of this size. From the diagram it can be seen that unless edges are detected on each signal at exactly the same instant, it is almost impossible to measure a zero phase difference between reference and generated signals. This is an intentional decision, \cite{idkwhattocite}.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\textwidth]{../new_pdet2}
	\caption[Inverter based \ac{TDL} RTL diagrams]{Inverter based \ac{TDL} RTL diagrams.}
	\label{fig:tdl_impl}
\end{figure}
The operation of the \ac{TDL} is as follows: A delayed version of the \texttt{count} signal acts as the clock for flip-flops forming each tap, which are rising edge activated. These flip-flops have a constant ``1'' at their $D$ inputs, so as the signal propagates through the delay line, each flip-flop with propagate a logic ``1'' to their corresponding \texttt{error_tap[i]} signal. When the measurement interval has completed, the \texttt{count} signal clocks the 15 bit wide \texttt{error_tap} signal into \texttt{error_tap_buff} which act as the output buffers of the \ac{PD}, holding the phase error constant between measurement intervals. As with the flip-flops performing edge detection, the flip-flops forming the taps are can only be used once before requiring a reset, which is again carried out using the \texttt[done] signal.

@@

Measurements were performed using an Agilent MSO7054A, a four channel, $4~\si[per-mode=symbol]{\giga\sample\per\second}$ oscilloscope. Signals were extracted over the regular \ac{PMOD} headers as the board does not provide outputs better suited to the measurement of signals that are available to the user, such as SMA or BNC connectors, and the \ac{PMOD} header for the analog-to-digital converter, which has lower impedance traces, is not available for the designer to re-configure. Data was acquired with the oscilloscope in quad channel mode at a sampling rate of $2\si{\giga\sample\per\second}$. One of the four channels was consumed by the external reference, leaving three open for signal measurements. $200\si{\micro\second}$ long captures were saved to an Agilent specified binary format which could be opened in Matlab for analysis.
%TODO diagram or picture of some sort

>>>>

%TODO eugene
The delay line itself is shown in Figure \ref{fig:tdl_impl}, with each tap implemented by a pair of flip-flops and three inverters. For an $N$ bit width phase error detection, $2^{N-1}-1$ taps are required. In the case of this \ac{ADPLL}, a 5 bit two's complement error signal is required, thus the range of the signal is $[-16,15]\cap\mathbb{Z}$. If the range is made symmetrical, 15 taps are required to fill a signal of this size. From the diagram it can be seen that unless edges are detected on each signal at exactly the same instant, it is almost impossible to measure a zero phase difference between reference and generated signals. This is an intentional decision, \cite{idkwhattocite}.
\begin{figure}[h]
	\centering
	\includegraphics[width=1.0\textwidth]{../new_pdet2}
	\caption[Inverter based \ac{TDL} RTL diagrams]{Inverter based \ac{TDL} RTL diagrams.}
	\label{fig:tdl_impl}
\end{figure}
The operation of the \ac{TDL} is as follows: A delayed version of the \texttt{count} signal acts as the clock for flip-flops forming each tap, which are rising edge activated. These flip-flops have a constant ``1'' at their $D$ inputs, so as the signal propagates through the delay line, each flip-flop with propagate a logic ``1'' to their corresponding \texttt{error\_tap[i]} signal. When the measurement interval has completed, the \texttt{count} signal clocks the 15 bit wide \texttt{error\_tap} signal into \texttt{error\_tap\_buff} which act as the output buffers of the \ac{PD}, holding the phase error constant between measurement intervals. As with the flip-flops performing edge detection, the flip-flops comprising the taps can only be used once before requiring a reset, which is again carried out using the \texttt{done} signal. As flip-flops have a hold time, the duration after the clock edge in which the signal applied at the $D$ input must not change to ensure valid data, an inverter is used to delay the reset to avoid this issue.

The output of the \ac{TDL} itself is not a binary signal, but rather the thermometer coded representation of the number of taps activated in the measurement interval. In order to convert to binary, the easiest solution is a switch statement, with an assignment performed based on the temperature code. However all \ac{ADPLL} blocks have been designed to be extensible, requiring the lookup to be generated at compile time. This is somewhat difficult to implement, and a simpler solution exists for this problem. In a \texttt{generate} statement, a variable size loop is used to count the number of nonzero bits as it would be done in C. At compile time this loop is converted into lookup tables, similarly to the switch statement.

The now unsigned binary representation of the error magnitude can be combined then with the sign bit to form a two's complement error signal. The file \textsc{PhaseDetectorDL.v} in Appendix \ref{adx:code} Listing \ref{lst:phase_detector_dl} contains the Verilog implementation of this module. \texttt{DONT\_TOUCH} compiler directives were used here in a number of places to ensure that the inverters and other elements that are key for timing are not removed in the synthesis process, as similarly to \ac{RO}, Vivado sees these as unneeded elements serving no purpose.

@@

Measurements were performed using an Agilent MSO7054A, a four channel, $4~\si[per-mode=symbol]{\giga\sample\per\second}$ oscilloscope. Signals were extracted over the regular \ac{PMOD} headers as the board does not provide outputs better suited to the measurement of signals that are available to the user, such as SMA or BNC connectors, and the \ac{PMOD} header for the analog-to-digital converter, which has lower impedance traces, is not available for the designer to re-configure. Data was acquired with the oscilloscope in quad channel mode at a sampling rate of $2\si{\giga\sample\per\second}$. One of the four channels was consumed by the external reference, leaving three free for signal measurements, in most cases the generated output of three \ac{ADPLL}s were connected. $200\si{\micro\second}$ long captures were saved to an Agilent specified binary format which could be opened in Matlab for analysis.
%TODO diagram or picture of some sort
